\textls[-0]{\thetitle}

### 2023-03-10 metatheory-condensed.tex
Fix.

The definitive version containing all the rules in \TT is stated in the appendix 
using debruijn indices and explicit substitution.
terms of a meta\-language supporting quotient inductive-inductive types
(QIITs)~\cite{nordvall2010inductive,altkap2016}.
QIITs support equality constructors, which facilitate the expression of
conversion rules (e.g., \ruleref{tmeq/sub/id}).
The formalization is available as a supplemental file in Agda syntax,
though it is not checked by Agda because Agda does not support QIITs
natively.
An effort to mechanize the formalization is underway, by following  \citet{altkap2016} 
to use quotient inductive-inductive types as 
the logical framework to state the syntax and using Agda's
\lsti{REWRITE} pragma to replace the limited uses of equality reflection appeared in 
an extensional meta\-logic.

>>>>

The definitive version containing all the rules in \TT is stated in the appendix 
using debruijn indices and explicit substitution.
An effort to mechanize the formalization is underway, by following  \citet{altkap2016} 
to use quotient inductive-inductive types as 
the logical framework to state the syntax and using Agda's
\lsti{REWRITE} pragma to replace the limited uses of equality reflection appeared in 
an extensional meta\-logic.
